Hierarchical Large Language Models for Multi-task problems

### 2024-01-12 paper/main.tex
Updates from Overleaf

\section{Introduction}
Low-Rank  Adaption (LoRA) of an existing large-scale pre-trained Large Language Models (LLM) \cite{hu_lora_2021} has become a popular go-to approach when solving a specific text problem.

@@

>>>>

\section*{Background}
Low-Rank  Adaption (LoRA) of an existing large-scale pre-trained Large Language Models (LLM) \cite{hu_lora_2021} has become a popular go-to approach when solving a specific text problem.

@@

\section{Introduction}
\section{Related works}
\section{Method: Hierarchical LLM}
\section{Experiments}
\section{Conclusion}
